Lens Modeling in \sw

### 2013-11-16 text/tex/intro.tex
save, go on sec 2

How to find gravitational lenses? Huge amount of image data from surveys that needs to be processed.
Even more coming in the future with new surveys \needcite
Robotic procession has been suggested \needcite, and tested \needcite, but has failed so far to be convincing \needcite.
Another suggestion involves humans, volountiers \footnote{A volounteer is considered everybody that has no background in astro physics.}.
\sw uses this approach with great succes so far.\needcite

>>>>

How to find gravitational lenses? Huge amount of image data from surveys that needs to be processed.
Even more coming in the future with new surveys \needcite
Robotic procession has been suggested \needcite, and tested \needcite, but has failed so far to be convincing \needcite.
Another suggestion involves humans, volunteers \footnote{A volunteer is considered everybody that has no background in astro physics.}.
\sw uses this approach with great success so far.\needcite
